---
title: "Central Medical Evaluation (CME) ICD-10 Agreement"
output: html_notebook
---

During the physician coding for Verbal Autopsies (VA), ICD-10 codes can be considered in agreement if they are within a certain ICD-10 code range.

This script processes data for ICD-10 blocks that determine the agreement between physician assigned ICD-10 codes from VAs.

## Libraries

```{r}
library(tidyverse)
library(cghrCodes)
```

## Read Data

Read data from `../data` folder:

* `icd10-equivalent-1.csv`: original ICD-10 equivalency file for reconciliation and adjudication provided by Rajeev Kamadod

```{r}
raw_file <- "../data/icd10-equivalent-1.csv"
cmea_raw <- read_csv(raw_file, show_col_types = FALSE)
cmea_raw
```

## Preprocess

Preprocesses the data by lowercasing all column names

```{r}
cmea <- cmea_raw %>% rename_all(tolower)
cmea
```

## Expand ICD-10 Ranges

Expands the ICD-10 codes from the `icdequivalence` column to create an ICD-10 code for each code block:

```{r}
cmeax <- expandICD10Data(
  cmea,
  icd10Column="icdequivalence",
  expandColumn="icd10_code"
)
cmeax
```

## Collapse ICD-10 Ranges

Collapse the individual ICD-10 ranges to add a short form column with consecutive ranges defined by `-`:

```{r}
cmea$icdequivalence_short <- apply(cmea, 1, function(x) paste(collapseICD10(x["icdequivalence"]), collapse=","))
cmea
```

## Save Data

Writes the collapsed and expanded CME ICD-10 agreement codes to the `../data` folder.

```{r}
write_csv(cmea, "../data/cmea10_raw.csv", na="")
write_csv(cmeax, "../data/cmea10xicd10_raw.csv", na="")
```
