---
title: "World Health Organization (WHO) 2016 Verbal Autopsy (VA) Codes"
output: rmarkdown::github_document
author:
- Bryan Gascon <bryan.gascon@mail.utoronto.ca>
- Richard Wen <rrwen.dev@gmail.com>
---

WHO VA 2016 codes to ICD mapping.

## Libraries

```{r}
library(tidyverse)
library(cghrCodes)
```

## Read Data

Read data from `../data` folder:

* `whovatoicd10mapping.csv`: original raw WHO VA mappings compiled from the WHO VA 2016 PDF manual by Bryan Gascon

```{r}
wva2016raw <- read_csv("../data/whovatoicd10mapping.csv", show_col_types=FALSE)
wva2016raw
```

## Preprocess

Preprocess the data by removing `VAs-` from the codes.

```{r}
wva2016 <- wva2016raw %>%
  rename_all(tolower) %>%
  mutate(who_va_code=str_remove(who_va_code, "^VAs-+"))
wva2016
```

## Collapse ICD-10 Ranges

Collapse the individual ICD-10 ranges to add a short form column with consecutive ranges defined by `-`:

```{r}
wva2016$icd_range_codes_2016_short <- apply(wva2016, 1, function(x) paste(collapseICD10(x["icd_range_codes_2016"]), collapse=","))
wva2016
```

## Expand ICD-10 Ranges

Expands the ICD-10 codes from the `icd_range_codes_2016` column to create an ICD-10 code for each WHO VA code:

```{r}
icd10towva2016 <- expandICD10Data(
  wva2016,
  icd10Column="icd_range_codes_2016",
  expandColumn="icd10_code"
)
icd10towva2016
```

## Save Data

Writes the collapsed and expanded WHO VA 2016 agreement codes to the `../data` folder.

```{r}
write_csv(wva2016, "../data/wva2016_raw.csv", na="")
write_csv(icd10towva2016, "../data/icd10towva2016_raw.csv", na="")
```
