---
title: "World Health Organization (WHO) 2022 Verbal Autopsy (VA) Codes"
output: html_notebook
author:
- Bryan Gascon <bryan.gascon@mail.utoronto.ca>
- Richard Wen <rrwen.dev@gmail.com>
---

WHO VA 2022 codes to ICD mapping.

## Libraries

```{r}
library(tidyverse)
library(cghrCodes)
```

## Read Data

Read data from `../data` folder:

* `whovatoicd10mapping.csv`: original raw WHO VA mappings compiled from the WHO VA 2022 PDF manual by Bryan Gascon

```{r}
wva2022raw <- read_csv("../data/whova2022toicd10mapping.csv", show_col_types=FALSE)
wva2022raw
```

## Preprocess

Preprocess the data by removing `VAs-` from the codes.

```{r}
wva2022 <- wva2022raw %>%
  rename_all(tolower) %>%
  mutate(who_va_code=str_remove(who_va_code, "^VAs-+"))
wva2022
```

## Collapse ICD-10 Ranges

Collapse the individual ICD-10 ranges to add a short form column with consecutive ranges defined by `-`:

```{r}
wva2022$icd_range_codes_short <- apply(wva2022, 1, function(x) paste(collapseICD10(x["icd_range_codes"]), collapse=","))
wva2022
```

## Expand ICD-10 Ranges

Expands the ICD-10 codes from the `icd_range_codes` column to create an ICD-10 code for each WHO VA code:

```{r}
icd10towva2022 <- expandICD10Data(
  wva2022,
  icd10Column="icd_range_codes",
  expandColumn="icd10_code"
)
icd10towva2022
```

## Save Data

Writes the collapsed and expanded WHO VA 2022 agreement codes to the `../data` folder.

```{r}
write_csv(wva2022, "../data/wva2022_raw.csv", na="")
write_csv(icd10towva2022, "../data/icd10towva2022_raw.csv", na="")
```
