---
title: "World Health Organization (WHO) 2016 Verbal Autopsy (VA) Codes"
output: rmarkdown::github_document
author:
- Richard Wen <rrwen.dev@gmail.com>
- Bryan Gascon <bryan.gascon@mail.utoronto.ca>
---

WHO VA 2016 codes from/to ICD mapping.

## Libraries

```{r}
library(tidyverse)
library(cghrCodes)
```

## Read Data

Read data from `../data` folder:

* `WVAtoICD_map1-5_RW.csv`: edited raw WHO VA mappings compiled from the WHO VA 2016 v1.5 PDF manual by Cheryl Chin

```{r}
wva2016raw <- read_csv(
  "../data/WVAtoICD_map1-5_RW.csv",
  show_col_types=FALSE,
  col_types = list(
    code = col_character(),
    group = col_character()
  )
)
wva2016raw
```

## Preprocess

Preprocess the data by lower-casing and renaming columns.

```{r}
wva2016 <- wva2016raw %>%
  rename_all(tolower) %>%
  relocate(
    kind,
    kind_depth,
    group,
    code,
    group_title,
    title,
    icd10_to,
    icd10_from_range,
    group_orig,
    code_orig,
    group_title_orig
  )
wva2016
```

## Collapse ICD-10 Ranges

Collapse the individual ICD-10 ranges to add a short form column with consecutive ranges defined by `-`:

```{r}
wva2016$icd10_from_range_short <- apply(wva2016, 1, function(x) paste(collapseICD10(x["icd10_from_range"]), collapse=","))
wva2016
```

## Expand ICD-10 Ranges

Expands the ICD-10 codes from the `icd_range_codes_2016` column to create an ICD-10 code for each WHO VA code:

```{r}

# Filter out codes only
icd10towva2016 <- wva2016 %>%
  filter(kind == "code") %>%
  select(
    group,
    code,
    group_title,
    title,
    icd10_from_range_short
  ) %>%
  rename(
    wva2016_group = group,
    wva2016_code = code,
    wva2016_group_title = group_title,
    wva2016_title = title,
    icd10_range = icd10_from_range_short
  )

# Expand icd codes
icd10towva2016 <- expandICD10Data(
  icd10towva2016,
  icd10Column="icd10_range",
  expandColumn="icd10_code"
)
as_tibble(icd10towva2016)
```

## Filter for WVA Codes Only

Filter for codes to create WVA 2016 to ICD 10 mappings, and also rename columns.

```{r}
wva2016toicd10 <- wva2016 %>% filter(kind == "code") %>%
  select(
    group,
    code,
    group_title,
    title,
    icd10_to
  ) %>%
  rename(
    wva2016_group = group,
    wva2016_code = code,
    wva2016_group_title = group_title,
    wva2016_title = title,
    icd10_code = icd10_to
  )
wva2016toicd10
```

## Save Data

Writes the collapsed and expanded WHO VA 2016 agreement codes to the `../data` folder.

```{r}
write_csv(wva2016, "../data/wva2016_raw.csv", na="")
write_csv(icd10towva2016, "../data/icd10towva2016_raw.csv", na="")
write_csv(wva2016toicd10, "../data/wva2016toicd10_raw.csv", na="")
```
